Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-01-23 WSSSPE1_report/WSSSPE1_summary_report.tex
adding a Makefile, make now should generate WSSPE1_summary_report.pdf make clean should clean up after latex
Minor edits.

\title[]{First Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE): Overview and Summary}

@@

\begin{abstract}
This technical report discusses the First Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE). ...
\end{abstract}

@@

the workshop organizers:
\begin{itemize}
\item "Daniel S. Katz" <dkatz@nsf.gov>
\item Gabrielle Allen <gdallen@illinois.edu>
\item "Neil Chue Hong" <N.ChueHong@software.ac.uk>
\item Manish Parashar <parashar@rutgers.edu>
\item David Proctor <dproctor@nsf.gov>
\end{itemize}

and additional volunteers:
\begin{itemize}
\item Chris Mattmann <chris.a.mattmann@jpl.nasa.gov>
\item Ketan Maheshwari <ketancmaheshwari@gmail.com>
\item Marlon Pierce <marpierc@iu.edu>
\item Colin Venters <C.Venters@hud.ac.uk>
\item Suresh Marru <smarru@iu.edu>
\item Lynn Zentner <lzentner@purdue.edu>
\item Anne Elster <anne.elster@gmail.com>
\item Shel Swenson <mdswenso@usc.edu>
\item Andy Ray Terrel <andy.terrel@gmail.com>
\item Abani Patra <abani.patra@gmail.com>
\item Nancy Wilkins-Diehr <wilkinsn@sdsc.edu>
\item James Spencer <j.spencer@imperial.ac.uk>
\item Frank Loeffler <knarf@cct.lsu.edu>
\item James Hetherington <j.hetherington@ucl.ac.uk>
\item "Sou-Cheng (Terrya) Choi" <sou.cheng.terrya.choi@gmail.com>
\item James Howison <james@howison.name>
\item Bruce Berriman <gbb@ipac.caltech.edu>
\item Hilmar Lapp <hlapp@nescent.org>
\item "Marcus D. Hanwell" <marcus.hanwell@kitware.com>
\item Lucas Nussbaum <lucas.nussbaum@loria.fr>
\item Matthew Turk <matthewturk@gmail.com>
\end{itemize}

@@

The First Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE1)\footnote{\url{http://wssspe.researchcomputing.org.uk/WSSSPE1}} was held on Sunday, 17 November 2013, in conjunction with the 2013 International Conference for High Performance Computing, Networking, Storage and Analysis (SC13)\footnote{\url{http://sc13.supercomputing.org}}.

@@

\section*{Appendix - List of attendees}

>>>>

\title[]{Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)}

@@

\begin{abstract}
This technical report discusses the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE). ...
\end{abstract}

@@

The workshop organizers:
\begin{itemize}
\item Daniel S. Katz <dkatz@nsf.gov>
\item Gabrielle Allen <gdallen@illinois.edu>
\item Neil Chue Hong <N.ChueHong@software.ac.uk>
\item Manish Parashar <parashar@rutgers.edu>
\item David Proctor <dproctor@nsf.gov>
\end{itemize}

Additional volunteers:
\begin{itemize}
\item Chris Mattmann <chris.a.mattmann@jpl.nasa.gov>
\item Ketan Maheshwari <ketancmaheshwari@gmail.com>
\item Marlon Pierce <marpierc@iu.edu>
\item Colin Venters <C.Venters@hud.ac.uk>
\item Suresh Marru <smarru@iu.edu>
\item Lynn Zentner <lzentner@purdue.edu>
\item Anne Elster <anne.elster@gmail.com>
\item Shel Swenson <mdswenso@usc.edu>
\item Andy Ray Terrel <andy.terrel@gmail.com>
\item Abani Patra <abani.patra@gmail.com>
\item Nancy Wilkins-Diehr <wilkinsn@sdsc.edu>
\item James Spencer <j.spencer@imperial.ac.uk>
\item Frank Loeffler <knarf@cct.lsu.edu>
\item James Hetherington <j.hetherington@ucl.ac.uk>
\item Sou-Cheng (Terrya) Choi <sou.cheng.terrya.choi@gmail.com>
\item James Howison <james@howison.name>
\item Bruce Berriman <gbb@ipac.caltech.edu>
\item Hilmar Lapp <hlapp@nescent.org>
\item Marcus D. Hanwell <marcus.hanwell@kitware.com>
\item Lucas Nussbaum <lucas.nussbaum@loria.fr>
\item Matthew Turk <matthewturk@gmail.com>
\end{itemize}

@@

The First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)\footnote{\url{http://wssspe.researchcomputing.org.uk/WSSSPE1}} was held on Sunday, 17 November 2013, in conjunction with the 2013 International Conference for High Performance Computing, Networking, Storage and Analysis (SC13)\footnote{\url{http://sc13.supercomputing.org}}.

@@

\appendix
\section{List of attendees}
